
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 2
        toc_float: true
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  2   
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  update,packages
---


## To update R packages,  use code in this file.

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = FALSE   ) # easier to read
```


```{r library, include=FALSE		}
file  <- knitr::current_input() 
library(jimTools)
``` 

### =========================
###   UPDATE  - 2 step process?
###   jimTools - has newer version of this
### =========================

## To update `old` packages
*   Appears that need to do this first, before update others
*   To increase `old` to include those comipiled earlier minor version of R
*   Use checkBuilt= T to force
*   Last resort:  remove old packages manually, then install

```{r update_old}
{
  begin  <- Sys.time()
  update.packages(ask = F,
                oldPkgs = old.packages(),
                checkBuilt=T)
  end  <- Sys.time()
  diff  <- end - begin
  diff
}
```

## To upgrade

vs update.packages() ?
```{r update2}

{
begin  <- Sys.time()
    update.packages(ask = FALSE , checkBuild=TRUE)
    end  <- Sys.time()
    diff  <- end - begin
    diff
}

```

```{r begin}
print(file)
```

***

```{r knit_exit(), include = FALSE  , eval=FALSE } 
# knitr::knit_exit()
```

\newpage


```{r render, eval=FALSE, include=FALSE 	} 
# TODO:  file is found when knitr runs (see above)

# file must be of form:
# dir/name_of_this_file    where dir is relative to project root

# NOTE:   .tex only works with PDF
# NOTE:    tex will NOT work with html
# in general, pdf will look nicer

file  <- "00030_update_R_packages.Rmd"
file

rmarkdown::render(file,
                  #output_format = "pdf_document",
                  output_format = "html_document",
                  output_file = "./out")
#                  output_file = "~/Downloads/print_and_delete/out")
```
