	 vim:linebreak:nowrap:nospell tw=78 fo=tqlnr foldcolumn=3 
	 
--- 
# Spaces, no Tabs
title: Template for .Rmd 
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 
---

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE) 
```

<!--  RENDER:  see bottom -->

```{r library, include=FALSE		}
library(jimTools)
``` 

BEGIN HERE (tibble, format etc)
```{r begin}
# all
options()
```

```{r options_tibble}
library(tibble)
library(tidyr)
library(purrr)
library(dplyr)

# 84 x 1  each element is named list
t <- tibble(options = options())
t
t$options["width"]

names(t$options[1])
names(t$options[2])
names(t$options[5])

# list of lists (mostly, not all, are vectors)
t$options

option_names  <- tibble(option_name = names(t$options))
option_names

pluck(t, 1, 1, 1)
pluck(t, 1, 2, 1)
pluck(t, 1, 5)


t$options[[10]]
t$options[[1]]


#### TODO
tidyr::unnest_wider(t$options)

```
```{r names}

#### another way
l  <- options()
names(l) #85

# random names, value
names(l[51])
l[51]


names(l[53])
l[67]

#### find element of vector
l["warning.length"]
l["pdfviewer"]	  # /usr/bin/xdg-open
l["keep.source"]  # TRUE
l["browser"]	 # croutonurlhandler
```



```{r versions}

#### 8- versions
packageVersion("rmarkdown") # 1.10
R.version.string     # 3.5.1
getwd()                 # ~/code/r_
list.files()            # list filesin wd
```

```{r dependencies}
# downstream
# For given <pkg>, what installed packages need it?	
pkg  <- "jimTools"
pkg  <- "tibble"
l <- tools::package_dependencies(
							pkg,
							db=installed.packages(),
							reverse=TRUE	)
l
# upstream
# For given <pkg>, what does pkgs MUST be installed? 
pkg  <- "jimTools"
pkg  <- "tibble"
l <- tools::package_dependencies(pkg, reverse=FALSE		)
l

#### dep is just content , a chr[]
	t  <- tibble(pkg = names(l), dep= purrr::pluck(l ))
	t




##	remove a pacakge
	##	not run
#remove.packages("cellranger")


######  011_update all packages - 
# available.packages()  	# A LOT!

# uncomment (takes time)
# update.packages(ask = FALSE, repos = 'https://cran.r-project.org')


###### 012_update knitr
install.packages('knitr', repos = c('https://xran.yihui.name', 'https://cran.r-project.org'))


##### 013_jennyBC
####  from https://github.com/smithjd/explore-libraries/blob/master/01_explore-libraries_jenny.R
ipt <- installed.packages() %>%
  as_tibble()

ipt %>% glimpse()
nrow(ipt)
dim(ipt)

####' 014_Exploring the packages

####   * tabulate by LibPath, Priority, or both
#### base: 14, recommended:15, my library:165
ipt %>%
  count(LibPath, Priority)

```{r knit_exit()} 
knitr::knit_exit() 
```
```{r getOption	}
getOption("width")

# set
options("jim_param"= 25)

# get
getOption("jim_param")
```


NOT WORKING
```{r environ}
jr_set_env(key = "name", value="jim")
jr_get_env("name")

Sys.setenv("name" = "jim")
Sys.getenv("name")
```


***

```{r knit_exit2()} 
knitr::knit_exit() 
```

/newpage

```{r render, eval=FALSE	} 
file <- "/home/jim/code/jimTools/rmd/004_set_options.Rmd"

file  <- basename(file) 
dir <-"rmd"

rmarkdown::render("~/code/jimTools/rmd/004_set_options.Rmd",
									output_format="pdf_document",
									output_dir="~/Downloads/print_and_delete/",
									output_file="out.pdf")

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
