TAGS:  jsonlite, FF bookmarks,
---
Compress and Archive Files on Laptop

TODO
	-	attr(); unlist(); 


```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
                      comment="      ##",  
                      error=TRUE, 
                      collapse=TRUE)
load_all()
library(jsonlite)
library(data.table)
library(magrittr)
setwd("~/code/jimTools/rmd")
```

#### walk down json
```{r}
b  <- fromJSON("~/Downloads/to_Drive/bookmarks-2022-08-24.json")



str(b, max.level=1, vec.len=5)

str(b$children, max.level=1, vec.len=2)

#	has 4 df
str(b$children$children, max.level=1, vec.len=2)

## Looks like bookmark folder ... then child with all the bookmarks

## 1st table (bookmarksmenu?) 17 x 12
str(b$children$children[[1]], max.level=1, vec.len=5)

df1  <- data.table(b$children$children[[1]])
df1 |> head()

## 2nd (toolbar)
str(b$children$children[[2]], max.level=1, vec.len=5)

str(b$children$children[[2]]$children[[7]]$children[[1]], max.level=1, vec.len=1)
df2  <- data.table(b$children$children[[2]])
df2[, .(title)]

##	multiple levels ! to get to Bayes
str(b$children$children[[2]]$children[[7]]$children[[1]], max.level=1, vec.len=1)

## next level
{
## grab milf
df2[title == "mlif"]
mlif_db  <- df2[title == "mlif"]$children
mlif_db  <- df2[title == "mlif"]$children[[1]]

## this is it.
mlif_db
is.data.frame(mlif_db)
# [1] TRUE
is.data.table(mlif_db)
# [1] FALSE
mlif_db  <- data.table(mlif_db)
str(mlif_db)
length(mlif_db)
mlif_db[[1]] |> head()
mlif_db[[2]] |> head()
mlif_db[[3]] |> head()

# yes!
mlif_db[, .(index,title)]
}
## 3rd (unfiled)
str(b$children$children[[3]], max.level=1, vec.len=5)
df3  <- data.table(b$children$children[[3]])
head(df3)

## 4th (mobile)
str(b$children$children[[4]], max.level=1, vec.len=5)



```


```{r render, eval=FALSE	}
file <- "001_compress_files.Rmd"
file  <- basename(file)
dir="rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```


## Which dir to backup?
```{r dir}
dir  <- "~/Downloads/documents"
dir

```


## Prepare prefix for compressed file
```{r prefix}
prefix  <- get_prefix()
prefix
```

## Prepare full-name of compressed file
```{r file_name}
out_file  <- get_compressed_file_name(prefix, dir)
out_file
```


jr_compress_dir()
```{r begin}

compress_dir(prefix, out_file, type="system", dir)


# dir = directory (under project root) 
jr_compress_dir(type = "project", dir = "rmd")
jr_compress_dir(type = "project", dir = "R")
```

### FAILS ...
### tar
*  add include/exclude files dir?
*  tar -tf <archive>   to list files

```{r tar}

    output_dir  <-  "~/Downloads/toGoogle"
    output_dir  <- here("rmd") 
    dir  <- here("~/Downloads/documents")  #  to backup
    out_file  <- "test_compress.tar.gz"
    tar( tarfile = paste0(output_dir, "/", out_file),
        files = dir,
        compression = c("gzip"),
        extra_flags = "-X  rmd/exclude_files.txt"
        )
```
TODO
* develop code HERE
* when good, put into compress.R

  - dotfiles, Except .Renviron are in git
  - 

  - Problems:  exclude/include certain files ?
```{r system_files}
# full list

the_dirs = list(
                bin = "~/bin/*.sh",
                mp3 = "~/Downloads/mp3", # scripts onl
                #dotfiles = "~/dotfiles/.Renviron",
                documents = "~/Downloads/documents" # multiple dirs


)

```

```{r tessting}
# pluck 1 dir at a time from the_dirs
dir = the_dirs[[3]]
dir

compress_dir(type="system", 
             dir = dir )

```

```{r}
# To inspect tar.gz
# tar doesn't like files in quotes
tar --list -f <file>
```




```{r knit_exit()}
knitr::knit_exit()
```

***







