---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding:  hide 
        toc: true 
        toc_depth: 4
        toc_float: true
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  2   
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  update,RPI,cleanup!,R_HOME, R_LIBS_USER
---

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE) 
library(data.table)
library(magrittr)
```

####  Problem

Normally, I use neovim + plugin nvim-R as my IDE.  Recently I tried to install
RStudio but ran into errors.


#### Directories

Seems each time I update R, I run into trouble with one or more directories
that R uses.   The reasons probably relate to the past of switching from RStudio to
neovim or compiling from source one time and using binaries the next.

Over time, my R setup has collected diretories with various permuations of "lib", "library", "local."
Rather than sort it all out, I decided to remove R and begin again. 

I found this the Ubuntu/Debian instructions helpful:
https://ftp.osuosl.org/pub/cran/bin/linux/debian, which explains some of R
environmental variables.


#### Organization


So here I collect useful R environment variables I found to be important.  To
ease navigation, I also set shell environment variables (I use zsh ) to match R.

Of course, your experience will differ, but getting a good grasp on the
R environment variables may avoid some future pain.

```{r data.table}
R_env  <- c("R_HOME", 
            "R_LIBS_USER", 
            "R_LIBS_SITE",
            NA,
            NA) 

paths  <- c("/usr/lib/R/",
            "/home/jim/R/x86_64-pc-linux-gnu-library/4.1/",
            "/usr/lib/R/library/",
            "/etc/R/Renviron",
            "~/.Renviron")

zsh_env  <- c("R_HOME", 
            "R_LIBS_USER", 
            "R_LIBS_SITE",
            NA,
            NA)



dt  <- data.table(R_env = R_env,
                  path = paths,
                  zsh_env = zsh_env)

```

```{r show_env}

dt %>% knitr::kable()
```

#### Special notes 
  *  Ending slash indicates a directory:   (/usr/lib/R/library/)
  *  No ending slash indicates a file:           ( ~/.Renviron )
  *  The file Renviron in directory /etc/R/   sets many environment variables,
    including $R_LIBS_SITE.  $R_LIBS_SITE is important because it designates a
    base one more directories for R packages.
  *  I pruned $R_LIBS_SITE to include only one directory:  /usr/lib/R/library/
  *  Because there are a couple of ways to install R packages (from Debian,
    from source, from inside R, ...) I may decide later to modify this. 
  *  (future) There are other environment variables that may be useful, for
    example R_ENVIRON, R_ENVIRON_USER but I did not use these.

#### Checking
Here is one way to confirm which directories R is using for packages.

```{r functions}
.libPaths()
```

####  Another way is through Sys.getenv() to find R env variables
  *  R_HOME
  *  R_LIBS_SITE
  *  R_LIBS_USER

```{r Sys, include=F}
s  <- Sys.getenv()
names  <- names(s)
head(names)
head(s[grep(pattern = "^R", x = names)])
s[grep(pattern = "^R_LIBS", x = names)]
```
```{r R_LiBS}

s[grep(pattern = "^R_LIBS", x = names)]
```

```{r help_files,include=F}
if (F) help(.libPaths)

```

####  Troubleshooting
  *  R --vanilla,  skips profile and any user set R environment variables.


```{r exit}
knitr::knit_exit()
```


## (got me into trouble) Upgrade R from 4.0.3 to 4.0.4
*  on Rpi 400
*  from source, *.tar.gz
*  follow directions (R install & admin guide)
*  tar -rf | .configure etc
*  last step    sudo make install, seemd to put it together (so running R
  opens 4.0.4
*  Directories !   Still confused.   No need to sweat.
*  3 directories most important,  ~/R/armv71.....-library/4.0/  (pkgs I add)
    /usr/local/lib/R/   where R prefers R_HOME be (leave it alone!)

*  run try_things_here/0088_base package commands. (shows which dir/which
  pkgs)





```{r render, eval=FALSE, include = F	} 
{
file <- "/home/jim/code/jimTools/rmd/0999_R_upgrade_notes.rmd"
file <- "rmd/0999_R_upgrade_notes.rmd"
file  <- basename(file)
file
file  <- paste0("rmd/",file)
file
}
file <- "rmd/0999_R_upgrade_notes.rmd"
rmarkdown::render(file, 
                  output_format="html_document",
                  #output_format="pdf_document",
                  output_dir="~/Downloads/print_and_delete")



```
