---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 2
        toc_float: true
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  2   
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  update,RPI,cleanup!,
---

## Upgrade R from 4.0.3 to 4.0.4
*  on Rpi 400
*  from source, *.tar.gz
*  follow directions (R install & admin guide)
*  tar -rf | .configure etc
*  last step    sudo make install, seemd to put it together (so running R
  opens 4.0.4
*  Directories !   Still confused.   No need to sweat.
*  3 directories most important,  ~/R/armv71.....-library/4.0/  (pkgs I add)
    /usr/local/lib/R/   where R prefers R_HOME be (leave it alone!)

*  run try_things_here/0088_base package commands. (shows which dir/which
  pkgs)

## Where am I?
```{r}

x  <- packageStatus()
print(x)
```

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE) 
library(jimTools) 
```

TODO   put this into R
prepend "0" to file names (put into jimTools)
```{r prepend_file_name}
# base tools only
prepend  <- "0"
the_dir  <- "rmd"
old  <- list.files(the_dir, pattern = "*.Rmd")
old
new  <- paste0(prepend, old)
new
if (FALSE )
file.rename(here(the_dir, old), 
            here(the_dir, new))

```
***

```{r knit_exit()} 
knitr::knit_exit() 
```

/newpage

```{r render, eval=FALSE	} 
file <- "rmd/0008_file_numbers.Rmd" 
file  <- basename(file) 
dir <-"rmd"

jimTools::ren_file(here(dir,file))
jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
